---
title: "Very Simple Examples Using Leaflet"
author: "David Hendry"
date: "11/1/2019"
output: html_document
---

```{r, echo=TRUE, eval=TRUE}
knitr::opts_chunk$set(echo = TRUE)
#----------------------------------------------
# Source the functions used in this example
#----------------------------------------------
source("leaflet_functions.R")

#----------------------------------------------
# Documentation and tutorials 
#    See https://rstudio.github.io/leaflet/
```

#### Example 1: Show Aukland, NZ
```{r aukland, echo=TRUE, eval=TRUE}
m <- leaflet() %>%
  addTiles() %>% 
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
m
```

#### Example 2: Show a place closer to home!!
```{r uw, echo=TRUE, eval=TRUE}
m <- get_basic_map_of_UW()
m
```

#### Example 3: Multiple cities and markers
```{r echo=TRUE, eval=TRUE}
cities <- get_city_data()
head(cities)
m <- get_map_with_city_markers(cities)
m
```

#### Example 4: Multiple cities and populations (numeric measurement type) mapped to circles, which vary in size with population
```{r echo=TRUE, eval=TRUE}
cities <- get_city_data()
m <- get_map_with_city_pop_circles(cities)
m
```

#### Example 5: Change the tiles to a different style
```{r echo=TRUE, eval=TRUE}
cities <- get_city_data()
m <- get_map_with_city_pop_circles(cities) %>%
addProviderTiles(providers$Stamen.Toner)
m
```

#### Example 6: Show a rectangle 
```{r echo=TRUE, eval=TRUE}
m <- get_map_with_rectangles()
m
```

#### The R code in `leaflet_functions.R` 
``````{r, eval=FALSE, code=readLines("./leaflet_functions.R")}
```